Analysis of Security-Cost Trade-off of Fully Homomorphic Encryption Schemes

### 2013-06-12 Report/article.tex
Avec changement d'algo

\begin{itemize}
\item Smart-Vercauteren scheme:\\
The scheme \cite{cryptoeprint:2009:571} has 3 parameters: ($N, \nu, \mu$ ). The somewhat homomorphic scheme uses 5 algorithms: (\texttt{KeyGen}, \texttt{Encrypt}, \texttt{Decrypt}, \texttt{Add}, \texttt{Mult}).
\begin{itemize}
\item \texttt{KeyGen}:
\begin{itemize}
\item $F(x)= x^{n}+1$
\item do
\begin{itemize}
\item $S(x)=_{R}(B_{\infty , N}(\nu/2)$
\item $G(x)=1+2.S(x)$
\item $p= resultant(G(x),F(x))$
\end{itemize}
until $p$ is prime
\item $D(x)=gcd(G(x),F(x))$ over $\mathbb{F}_p[x]$
\item $\alpha$: the unique root of $D(x)$
\item apply \texttt{fmpz\_poly\_xgcd} to obtain $Z(x)$ such that $Z(x).G(x)=p$ mod $F(x)$
\item $B=z_0$ mod $2p$
\item $PK = (p, \alpha)$ and $Sk = (p , B)$
\end{itemize}
\item \texttt{Encrypt}($m \in \{0,1\} , PK$):
\begin{itemize}
\item $R(x)=_{R}(B_{\infty , N}(\mu/2)$
\item $C(x)=m+2.R(x)$
\item $c=C(\alpha) mod p$
\item return $c$
\end{itemize}
\item \texttt{Decrypt}($c, SK$):
\begin{itemize}
\item $m= (c - round(c.B/p)) mod 2$
\item return $m$
\end{itemize}
\item \texttt{Add}($c_1$, $c_2$, $PK$):
\begin{itemize}
\item $c_3=c_1+c_2 mod p$
\item return $c_3$
\end{itemize}
\item \texttt{Mult}($c_1$, $c_2$, PK):
\begin{itemize}
\item $c_3=c_1.c_2 mod p$
\item return $c_3$
\end{itemize}
\end{itemize}
\item BGV:
\end{itemize}
\subsection{Considered Implementations}

@@

\section{Evaluation on the benchmarks}
Measurements by varying the parameters or the plaintext size.
\section{Analysis of the results}

>>>>

Smart-Vercauteren scheme:\\
The scheme \cite{cryptoeprint:2009:571} has 3 parameters: ($N, \nu, \mu$ ). The somewhat homomorphic scheme uses 5 algorithms: (\texttt{KeyGen}, \texttt{Encrypt}, \texttt{Decrypt}, \texttt{Add}, \texttt{Mult}).

 \KwData{$N, \nu, \mu$ }

 \KwResult{$pk, sk$}

  $F(x)= x^{n}+1$

 \While{$p$ is not prime}{

	$S(x)=_{R}(B_{\infty , N}(\nu/2)$\;

	$G(x)=1+2.S(x)$\;

	$p= resultant(G(x),F(x))$\;

 	$D(x)=gcd(G(x),F(x))$ over $\mathbb{F}_p[x]$\;

	$\alpha$: the unique root of $D(x)$\;

 	apply \texttt{fmpz\_poly\_xgcd} to obtain $Z(x)$ such that $Z(x).G(x)=p$ mod $F(x)$\;

	$B=z_0$ mod $2p$\;

	$pk = (p, \alpha)$ and $sk = (p , B)$\;

return($pk$, $sk$)

\end{algorithm}
\texttt{Encrypt}($m \in \{0,1\} , PK$): 
\newline \phantom{x}\hspace{3ex}  $R(x)=_{R}(B_{\infty , N}(\mu/2)$
 \; $C(x)=m+2.R(x)$ 
\newline \phantom{x}\hspace{3ex} return  $c=C(\alpha) mod p$
\newline \texttt{Decrypt}($c, SK$):
\newline \phantom{x}\hspace{3ex} $m = (c - round(c.B/p)) mod 2$;
\phantom{x}\hspace{1ex} return $m$

\texttt{Add}($c_1$, $c_2$, $PK$):
\newline \phantom{x}\hspace{3ex} $c_3=c_1+c_2 mod p$
  \phantom{x}\hspace{1ex}  return $c_3$
\newline \texttt{Mult}($c_1$, $c_2$, PK):
 \newline \phantom{x}\hspace{3ex}  $c_3=c_1.c_2 mod p$
 ; \phantom{x}\hspace{1ex}  return $c_3$
\subsection{Considered Implementations}

@@

\section{Evaluation on the benchmarks}
Measurements by varying the parameters or the plaintext size.

\begin{figure*}

\incudegraphics{"/home/honey/Documents/Mosig\_1/ProjSpec/Measurements\Insertion\_sort\_CPU.jpg"}

\end{figure*}

\section{Analysis of the results}
